---
title: "DDS_CS2_U15_rmd"
author: "Dawn Bowerman"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#install package and load library
#install.packages("class")
#install.packages("caret")
#install.packages("e1071")
library(class)
library(caret)
library(e1071)
library(tidyverse)
library(scales)
library(ggplot2)




CaseStudy2_notnadata <- CaseStudy2_data %>% filter(!is.na(Attrition)) #Filter out rows with missing data

view(CaseStudy2_notnadata)


CS2YesAttrition <- CaseStudy2_data %>% filter(Attrition == "Yes")
view(CS2YesAttrition)



CaseStudy2_data_asFactor <- as.factor(CaseStudy2_data$BusinessTravel)

summary(CaseStudy2_data_asFactor)




CS2YesAttritselect <- CS2YesAttrition %>% select(Age, DistanceFromHome, EnvironmentSatisfaction, HourlyRate,
JobSatisfaction, Education, DailyRate, JobInvolvement, MonthlyIncome, JobLevel, MonthlyRate, NumCompaniesWorked,
PercentSalaryHike, PerformanceRating, RelationshipSatisfaction, YearsWithCurrManager,WorkLifeBalance, YearsInCurrentRole, YearsAtCompany, StockOptionLevel)

view(CS2YesAttritselect)

CS2YesAttrition %>% ggplot(mapping = aes(x = JobRole, fill = JobRole)) + geom_bar() + coord_polar() + ggtitle("Polar Bar Chart of Job Role - Yes Attrition Counts")




CS2Attritselect <- CaseStudy2_data %>% select(Age, DistanceFromHome, EnvironmentSatisfaction, HourlyRate,
                                                 JobSatisfaction, Education, DailyRate, JobInvolvement, MonthlyIncome, JobLevel, MonthlyRate, NumCompaniesWorked,
                                                 PercentSalaryHike, PerformanceRating, EmployeeCount, WorkLifeBalance, YearsWithCurrManager, RelationshipSatisfaction)

view(CS2Attritselect)




CS2YesAttritselectAs_Factor <- as.factor(CaseStudy2_data[4, 6, 9, 13, 17, 19])


                                        
View(CS2YesAttritselectAs_Factor)








# Possible to make as.factors

library(tidyverse)
library(scales)

df <- data.frame(
  Region = as.factor(c("Wellington", "Bay of Plenty", "Bay of Plenty",
                       "Manawatu-Wanganui", "Auckland", "Wellington",
                       "Canterbury", "Northland", "Canterbury", "Canterbury",
                       "Canterbury", "Wellington", "Hawke's Bay",
                       "Bay of Plenty", "Waikato", "Manawatu-Wanganui", "Canterbury",
                       "Wellington", "Auckland", "Manawatu-Wanganui"))
)


# Percent AGE Bar graph


CS2YesAttritselect %>% 
  count(Age) %>% 
  mutate(prop = n/sum(n)) %>% 
  ggplot(aes(x = Age, y = prop)) +
  geom_col(fill = "#FF7F24") +
  geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of Age in YES Attrition") +
  coord_cartesian(clip = "off") +
  scale_y_continuous(labels = percent_format()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
        axis.title = element_blank(),
        plot.margin = margin(t = 20, r = 10, b = 10, l = 10))



  # Percent DistanceFromHome Bar graph
  
  
  CS2YesAttritselect %>% 
    count(DistanceFromHome) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = DistanceFromHome, y = prop)) +
    geom_col(fill = "deepskyblue") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of DistanceFromHome in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))



  # Percent EnvironmentSatisfaction Bar graph
  
  
  CS2YesAttritselect %>% 
    count(EnvironmentSatisfaction) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = EnvironmentSatisfaction, y = prop)) +
    geom_col(fill = "darkviolet") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of EnvironmentSatisfaction in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))





  
  # Percent HourlyRate Bar graph
  
  
  CS2YesAttritselect %>% 
    count(HourlyRate) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = HourlyRate, y = prop)) +
    geom_col(fill = "yellow") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of HourlyRate in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))

  
  

  # Percent JobSatisfaction Bar graph
  
  
  CS2YesAttritselect %>% 
    count(JobSatisfaction) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = JobSatisfaction, y = prop)) +
    geom_col(fill = "red") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of JobSatisfaction in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))




  # Percent Education Bar graph
  
  
  CS2YesAttritselect %>% 
    count(Education) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = Education, y = prop)) +
    geom_col(fill = "springgreen") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of Education in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))




  # Percent JobInvolvement Bar graph
  
  
  CS2YesAttritselect %>% 
    count(JobInvolvement) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = JobInvolvement, y = prop)) +
    geom_col(fill = "cyan") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of JobInvolvement in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  
  
  
  # Percent JobLevel Bar graph
  
  
  CS2YesAttritselect %>% 
    count(JobLevel) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = JobLevel, y = prop)) +
    geom_col(fill = "#067191") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of JobLevel in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  
  
  # Percent NumCompaniesWorked Bar graph
  
  
  CS2YesAttritselect %>% 
    count(NumCompaniesWorked) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = NumCompaniesWorked, y = prop)) +
    geom_col(fill = "#F0BF1D") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of NumCompaniesWorked in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  
  # Percent RelationshipSatisfaction Bar graph
  
  
  
  CS2YesAttritselect %>% 
    count(RelationshipSatisfaction) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = RelationshipSatisfaction, y = prop)) +
    geom_col(fill = "#DFFF00") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of RelationshipSatisfaction in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  # Percent YearsWithCurrManager Bar graph 
  
  CS2YesAttritselect %>% 
    count(YearsWithCurrManager) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = YearsWithCurrManager, y = prop)) +
    geom_col(fill = "#DE3163") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of YearsWithCurrManager in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  # Percent WorkLifeBalance Bar graph
  
  
  CS2YesAttritselect %>% 
    count(WorkLifeBalance) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = WorkLifeBalance, y = prop)) +
    geom_col(fill = "#e3740c") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of WorkLifeBalance in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  # Percent YearsInCurrentRole Bar graph
 
  CS2YesAttritselect %>% 
    count(YearsInCurrentRole) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = YearsInCurrentRole, y = prop)) +
    geom_col(fill = "#CCCCFF") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of YearsInCurrentRole in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  # Percent YearsAtCompany Bar graph
  
  
  CS2YesAttritselect %>% 
    count(YearsAtCompany) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = YearsAtCompany, y = prop)) +
    geom_col(fill = "#26af1c") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of YearsAtCompany in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  
  # Percent StockOptionLevel Bar graph
  
  
  CS2YesAttritselect %>% 
    count(StockOptionLevel) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = StockOptionLevel, y = prop)) +
    geom_col(fill = "#1e5dfa") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of StockOptionLevel in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  # Percent PercentSalaryHike Bar graph
  
  
  CS2YesAttritselect %>% 
    count(PercentSalaryHike) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = PercentSalaryHike, y = prop)) +
    geom_col(fill = "#fa1eb1") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of PercentSalaryHike in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10))
  
  
  
  
  
  
  # Percent PercentSalaryHike ***As Factor*** Bar graph
  
  
  CS2YesAttritselectAsFactor %>% 
    count(PercentSalaryHike) %>% 
    mutate(prop = n/sum(n)) %>% 
    ggplot(aes(x = PercentSalaryHike, y = prop)) +
    geom_col(fill = "#fa1eb1") +
    geom_text(aes(label = percent(prop)), vjust = -1) + ggtitle("Percent of PercentSalaryHike in YES Attrition") +
    coord_cartesian(clip = "off") +
    scale_y_continuous(labels = percent_format()) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=45, hjust=1, vjust = 1),
          axis.title = element_blank(),
          plot.margin = margin(t = 20, r = 10, b = 10, l = 10)) 
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
```{r}
  
  CS2AttritselectKNN <- CaseStudy2_data %>% select(Attrition, Age, DistanceFromHome, EnvironmentSatisfaction, HourlyRate,
                                                JobSatisfaction, Education, DailyRate, JobInvolvement, MonthlyIncome, JobLevel, MonthlyRate, NumCompaniesWorked,
                                                PercentSalaryHike, PerformanceRating, EmployeeCount, RelationshipSatisfaction, YearsWithCurrManager,WorkLifeBalance,
                                                YearsInCurrentRole, StockOptionLevel, PercentSalaryHike)
  
  
  view(CS2AttritselectKNN)
  
  
# KNN model numbers only

set.seed(1)
iterations = 500
numks = 90
splitPerc = .70

masterAcc = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  trainIndices = sample(1:dim(CS2AttritselectKNN )[1],round(splitPerc * dim(CS2AttritselectKNN )[1]))
  train = CS2AttritselectKNN [trainIndices,]
  test = CS2AttritselectKNN [-trainIndices,]
  for(i in 1:numks)
  {
    classifications = knn(train[,c(2:21)],test[,c(2:21)],train$Attrition, prob = TRUE, k = i)
    table(classifications,test$Attrition)
    CM = confusionMatrix(table(classifications,test$Attrition))
    masterAcc[j,i] = CM$overall[1]
  }
  
}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l")    



confusionMatrix(table(knn.cv(CS2AttritselectKNN [,2:21],CS2AttritselectKNN $Attrition, k = 30), CS2AttritselectKNN $Attrition))
QOI = data.frame(JobLevel = 1,WorkLifeBalance = 3)
knn(CS2AttritselectKNN [,2:21],QOI,CS2AttritselectKNN $Attrition, prob = TRUE, k = 30)


QOI = data.frame(JobLevel = 1,WorkLifeBalance = 3)
```

```{r}








read.csv(CaseStudy2_data)


# KNN model All factors

set.seed(1)
iterations = 500
numks = 90
splitPerc = .70

masterAcc = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  trainIndices = sample(1:dim(CaseStudy2_data)[1],round(splitPerc * dim(CaseStudy2_data)[1]))
  train = CaseStudy2_data [trainIndices,]
  test = CaseStudy2_data [-trainIndices,]
  for(i in 1:numks)
  {
    classifications = knn(train[,c(2,32)],test[,c(2,32)],train$Attrition, prob = TRUE, k = i)
    table(classifications,test$Attrition)
    CM = confusionMatrix(table(classifications,test$Attrition))
    masterAcc[j,i] = CM$overall[1]
  }
  
}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l")    



confusionMatrix(table(knn.cv(CaseStudy2_data [,4:36],CaseStudy2_data $Attrition, k = 30), CaseStudy2_data $Attrition))
QOI = CaseStudy2CompSet_No_Attrition
knn(CaseStudy2_data [,4:36],QOI,CaseStudy2_data $Attrition, prob = TRUE, k = 30)



```

```{r}
























# naiveBayes with CaseStudy2data


AttritionBayes = read.csv(CaseStudy2_data,header = TRUE)
AttritionBayes

install.packages("e1071") #naiveBayes()
library(e1071)

model = naiveBayes(Attrition~.,data = AttritionBayes)
predict(model,AttritionBayes[,c(2,5,7,8,12,14,15,16,18,22,25,26,27,29:36)])

df = CaseStudy2CompSet_No_Attrition
predict(model,df) #just classifications
CaseStudy2CompSetLabeled <- predict(model,df, type = "raw") #gives probabilities 

view(CaseStudy2CompSetLabeled)

CaseStudy2CompSetLabeledNum <- cbind(CaseStudy2CompSetLabeled, CaseStudy2CompSet_No_Attrition$ID, make.row.names = TRUE,)
view(CaseStudy2CompSetLabeledNum)


write.csv(CaseStudy2CompSetLabeledNum,"H:/Schools/SMU/DoingDataScienceHomework/UnitOne/Unit One/Unit 14 and 15 Case Study 2/CaseStudy2PredictionsBowermanAttrition.csv", row.names = FALSE)

# Make your own dataframe:

# df = data.frame(JobLevel = "1", NumCompaniesWorked = "1", YearsWithCurrManager = 0, Education = 3, WorkLifeBalance = 3)
# predict(model,df) #just classifications
# predict(model,df, type = "raw") #gives probabilities 
```






    

# comparison 3D graph with Attrition colored

library(plotly)


p <- plot_ly(CaseStudy2_data, x = ~WorkLifeBalance, y = ~StockOptionLevel, z = ~JobLevel, color = ~Attrition) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'WorkLifeBalance'),
                      yaxis = list(title = 'StockOptionLevel'),
                      zaxis = list(title = 'JobLevel')))
p


```


```


#   linear model of CaseStudy2CompSet for Salary
```{r}
library(tidyverse)
library(reshape2)


CaseStudy2_data %>% 
  ggplot(aes(x = JobRole, y = MonthlyIncome)) + geom_point() + 
  ggtitle("CaseStudy2_data: YearsAtCompany v. MonthlyIncome") + geom_smooth(method = "lm")
  

# degree 1 model
fit = lm(MonthlyIncome~JobRole + JobLevel + Age, data = CaseStudy2_data)
summary(fit)

preds = predict(fit, newdata = CaseStudy2CompSet_No_Salary)
preds
CaseStudy2Predictions_Salary <- preds


CaseStudy2Predictions_Bowerman_Salary <- cbind(CaseStudy2PredictionsBowerman_Salary, CaseStudy2CompSet_No_Salary$ID)


view(CaseStudy2Predictions_Bowerman_Salary)


write.csv(CaseStudy2Predictions_Bowerman_Salary,"H:/Schools/SMU/DoingDataScienceHomework/UnitOne/Unit One/Unit 14 and 15 Case Study 2/CaseStudy2Predictions_Bowerman_Salary.csv", row.names = TRUE)



